---
title: New website
author: Claus Gaarde Pedersen
date: '2017-02-14'
categories:
    - R
    - Github
    - Hugo
tags:
    - R
    - Github
description: 'First post'
draft: yes
---

Welcome to this new website using Github pages with Rstudio/blogdown and Hugo
Actually its my first time ever trying to my own website.  
With more than 20 year experience in the it-business, maybe you would have expected that  
to have happened sooner.

Reading up on this new thing with making a webpage through rstudio with blogdown and Hugo caugth my interested.  
Finally i should use the time needed to set that up, because this seems to be a good avenue to show the things that can be made through Rmarkdown.

Bellow is my first at it. It seems that there is work to do to have the tabsets working, but you can see an example leaflet, which i predict you will see alot of on this site further on.

# {.tabset .tabset-fade .tabset-pills}

## Map

```{r ref.label="code", echo=FALSE}

```

## Code

```{r code, eval=FALSE}
library(leaflet)
leaflet() %>% addTiles()
```


